---
title: "Week 2 Demonstration"
format: html
editor: visual
---

## Set up

We always load the following packages.

```{r}
#| message: FALSE
library(fpp3)
library(tidyverse)
```

## 1. Lags and differencing

Consider the `aus_arrivals` dataset and try to plot lagged arrival values. What is strange about this plot? How can you fix it?

## 2. Moving averages

Using the arrivals from Japan time series within `aus_arrivals`, do the following.

-   Compute a moving average with window size 2 using two different methods: using `slide_dbl` and manually (i.e. without using `slide_dbl`). Show that you get the same answer.

-   Plot moving averages with a few different window sizes to see the effect of varying the window size. Which window size would you pick?

## 3. Log transform and differencing

Let's consider the sales of diabetes drugs in Australia. The following code loads and plots this time series.

```{r}
diabetes <- read_rds("../_data/cleaned/diabetes.rds")
diabetes |> autoplot()
```

-   Apply a log transformation and plot the result. What does it do to the seasonal fluctuations?

-   Take a difference of the log transformed time series. What is the meaning of the resulting time series?

-   Take a seasonal difference of the log transformed time series. What is the meaning of the resulting time series? How does it compare with the time series obtained in the previous part?

## 4. Computing classical decomposition

Compute a classical decomposition for the following time series without using the `classical_decomposition()` function.

```{r}
aus_arrivals_jap <- aus_arrivals |>
  filter(Origin == "Japan") |>
  select(Quarter, Arrivals)
```

## 5. Classical vs STL decomposition

Start with the following code snippet creating a time series of passengers flying on Ansett Airlines. Perform classical and STL decompositions and comment on their differences. Which do you trust more?

```{r}
melsyd_economy <- ansett |>
  filter(Airports == "MEL-SYD", Class == "Economy") |>
  mutate(Passengers = Passengers/1000)
autoplot(melsyd_economy, Passengers) +
  labs(y = "Passengers ('000)")
```

## 
